Community Detection Methods for Generalized Random Dot Product Graphs

### 2021-05-29 proposal/slides.Rmd
updated slides

---
title: Community Detection Methods for Generalized Random Dot Product Graphs
subtitle: Dissertation Proposal
author: 
  - John Koo$^1$
  - Michael Trosset$^1$
  - Minh Tang$^2$
  - Julia Fukuyama$^1$
  - Roni Khardon$^3$
  - Fangzheng Xie$^1$
institute:
  - $^1$Indiana University, Department of Statistics
  - $^2$North Carolina State University, Department of Statistics
  - $^3$Indiana University, Department of Computer Science
date: 'June 2021'
output: 
  beamer_presentation:
    fig_crop: no
    theme: 'default'
    colortheme: 'beaver'
    includes:
      in_header: page_headers.tex
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,ruled,vlined]{algorithm2e} 
- \setcitestyle{numbers,square,comma}
- \usepackage{verbatim}
- \usepackage{amsthm}
- \usepackage{comment}
---

@@

>>>>

---
output: 
  beamer_presentation:
    fig_crop: no
    theme: 'default'
    colortheme: 'beaver'
    includes:
      in_header: 
        - page_headers.tex
        - slidestemplate.tex
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,ruled,vlined]{algorithm2e} 
- \setcitestyle{numbers,square,comma}
- \usepackage{verbatim}
- \usepackage{amsthm}
- \usepackage{comment}
---

@@

## {.plain}

\center

\LARGE

\textcolor{darkred}{Community Detection Methods for the Generalized Random Dot Product Graph}

\normalsize

Dissertation Proposal

June 2021

John Koo^1^  
*PhD Candidate*

*Research Committee*  
Dr. Michael Trosset^1^  
Dr. Minh Tang^2^  
Dr. Julia Fukuyama^1^  
Dr. Roni Khardon^3^  
Dr. Fangzheng Xie^1^

\tiny

^1^Department of Statistics, Indiana University  
^2^Department of Statistics, North Carolina State University  
^3^Department of Computer Science, Indiana University

\normalsize
